---
title: "Superbowl Predictions"
output: html_notebook
---
# By Diomides Suero 
# Loading library and packages
```{r}
library(tidyverse)
library(ggplot2)
```
# Uploading data set 

```{r}
# reading file as csv
SB<-read_csv("spreadspoke_scores.csv")
SB
```
# filtering data for 2021-2022 regular season
```{r}
# Filtering year 2019-present
year<-filter(SB, schedule_season>=2021)
year
```

# Filtering data from 2021-present just bengals and rams
```{r}
# rams at home
homeRams<-filter(year,team_home== "Los Angeles Rams")
homeRams

# bengals away
awayBengals<-filter(year, team_away=="Cincinnati Bengals")
awayBengals
```
# Prediction 1: will Rams win because of home advantage? 
```{r}

#histogram
ggplot(data = homeRams) + geom_histogram(mapping = aes(x = score_home, fill=team_away), bins = 15) + 
  labs(title = "Rams Home Games Advantage",
x = "Score", y = "Count")
ggplot(data = homeRams) + geom_histogram(mapping = aes(x = score_away, fill=team_away), bins = 15) + 
  labs(title = "Rams Home Games vs Opposite Team Scores",
x = "Score", y = "Count")


```

# average scores, Rams when at home
```{r}
summary(homeRams)
```
# Prediction 2: will Bengals lose because Rams have home advantage? 
```{r}

#histogram
ggplot(data = awayBengals) + geom_histogram(mapping = aes(x = score_home, fill=team_home), bins = 15) + 
  labs(title = "Opposite Team Home Games Scores",
x = "Score", y = "Count")
ggplot(data = awayBengals) + geom_histogram(mapping = aes(x = score_away, fill=team_home), bins = 15) + 
  labs(title = "Bengals Away Scores",
x = "Score", y = "Count")


```
# average scores, Bengals when away
```{r}
summary(awayBengals)
```

# Filtering data from 2021-present just bengals and rams against same team
```{r}
# rams
rams<-filter(year,team_home== "Los Angeles Rams")
rams

# bengals
bengals<-filter(year, team_away=="Cincinnati Bengals")
bengals
```
# Visualization 3: Common Teams they played against Rams(home), Bengals (Away)
```{r}

#histogram

ggplot(data = rams) + geom_histogram(mapping = aes(x = score_home, fill=team_away), bins = 15) + 
  labs(title = "Rams Home Games Advantage",
x = "Score", y = "Count")

ggplot(data = bengals) + geom_histogram(mapping = aes(x = score_home, fill=team_home), bins = 15) + 
  labs(title = "Bengals Away Game scores",
x = "Score", y = "Count")

```

